The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2019-09-26 tex/VHzQ.tex
VHzQ tiny update

  We query the WSA and VSA performing matched-aperture photometry at
  the positions of our {\bf 488} VH$z$Qs. This database is world-readable and
  we give the full recipe and relevant SQL queries for accessing both
  databases in Appendix~\ref{sec:SQL} as well as online.

@@

Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections for each VH$z$Q. 
There are 60 quasars with over 100 NEOWISE-R epochs, nine with over 200 epochs and four with over 300.
Figure~\ref{fig:MIR_LC_3egs} presents three examples of the brighter MIR objects with well-sampled 
MIR lightcurves and associated colour changes; 
SDSS J0100+2802 (Fig.~\ref{fig:MIR_LC_3egs} top), 
SDWISE  J1752+5036    (middle), 
SDSS J1621+5155 (bottom). 
For the light curves, we show weighted means for every 6 month NEOWISE-R scan.
Due to the WISE scanning pattern, objects close to the North Ecliptic Pole 
are well sampled, and indeed this is the area for further investigation 
time-domain investigation with upcoming large infrared space telescopes
\citep{Jansen2018, White2019AAS}.

@@

At the \href{http://horus.roe.ac.uk/vsa/login.html}{VSA Login}, enter 
with these credentials::
\begin{itemize}
    \item Username: {\tt VSERV1000} 
    \item password: {\tt highzqso} 
    \item community: {\tt proprietary}
\end{itemize}
Then the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL
Query} page is where the database release to use is {\tt
VSERV1000v20190508}. The queries are the same as those used in the
WSA, see Appendix~\ref{sec:SQL}, but the names of the tables starting
with {\tt wserv1000} should be replaced with {\tt vserv1000}.

>>>>

  We query the WSA and VSA performing matched-aperture photometry at
  the positions of our {\bf 488} VH$z$Qs. This database is
  world-readable and we give the full recipe and relevant SQL queries
  for accessing both databases in Appendices~\ref{sec:SQL_WSA}
  and~\ref{sec:SQL_VSA} as well as online.

@@

Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections for each VH$z$Q. 
There are 60 quasars with over 100 NEOWISE-R epochs, nine with over 200 epochs and four with over 300.
Figure~\ref{fig:MIR_LC_3egs} presents three examples of the brighter MIR objects with well-sampled 
MIR lightcurves and associated colour changes; 
SDSS J0100+2802 (Fig.~\ref{fig:MIR_LC_3egs} top), 
SDWISE  J1752+5036    (middle), 
SDSS J1621+5155 (bottom). 
For the light curves, we show weighted means for every 6 month NEOWISE-R scan.
Due to the WISE scanning pattern, objects close to the North Ecliptic Pole 
are well sampled, and indeed this is the area for further investigation 
time-domain investigation with upcoming large infrared space telescopes
\citep{Jansen2018, WhiteC2019AAS}.

@@

At the \href{http://horus.roe.ac.uk/vsa/login.html}{VSA Login}, enter 
with these credentials::
\begin{itemize}
    \item Username: {\tt VSERV1000} 
    \item password: {\tt highzqso} 
    \item community: {\tt proprietary}
\end{itemize}
Then the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL
Query} page is where the database release to use is {\tt
VSERV1000v20190508}. The queries are the same as those used in the
WSA, see Appendix~\ref{sec:SQL_WSA}, but the names of the tables starting
with {\tt wserv1000} should be replaced with {\tt vserv1000}.
